\LARGE \bf Constrained Attitude Control

### 2015-09-19 manuscript.tex
updating outline

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
introduction to attitude dynamics problem

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

Spacecraft are complicated electro mechanical devices and have become critical to national security.
Spacecraft operations require extensive planning periods and human interaction to perform.
The ability to robustly and autonomously plan and execute complicated spacecraft maneuvers can drastically improve the performance and duty cycle of assets.
One key technology to enable spacecraft autonomy is the execution of large angular slews in the presence of constraints.
For example, many spacecraft missions are equipped with sensitive optical instruments that require targeting while simultaneously avoiding direct exposure to sunlight.
One of the distinct features of the attitude dynamics of a rigid body is that it evolves on a nonlinear manifold.
The special orthogonal group, \( \SO \), yields unique properties that are not present in dynamic systems on a linear space. 
In addition, the removal of constrained zones from the rotational configuration space results in a non-convex and more complicated system.
The attitude dynamics and control of spacecraft without constraint has been extensively studied in the literature.
This work builds upon previous results to include attitude constraints on \( \SO \).

In this work an attitude control system is presented to track a desired trajectory while avoiding constrained regions. 
The control system is formulated directly on the nonlinear manifold \( \SO \) and avoids the issues associated with minimal representations.
The approach is based on a logarithmic barrier potential function developed directly on \( \SO \). 
This avoids the singularities associated with Euler angles~\cite{mcinnes1994}.
Euler angles are not suitable for large angle slew maneuvers as the type of Euler angle sequence should be switched to avoid the singular regions.
Quaternions do not suffer from singularities but as the three-sphere double covers the special orthogonal group, there exists two antipodal points on the three-sphere which represents an equivalent attitude.
As a result, control schemes based on quaternions should carefully resolve this ambiguity to avoid unwinding, where a rigid body unnecessarily rotates through a large angle in spite of a small initial error.~\cite{lee2011b}.

introduction to attitude dynamics problem
